---
title: "Complete integers"
author: "Davide Peressoni"
date: "May-June 2022"
description: "TODO"

url: https://dpdmancul.gitlab.io/complete-integers-agda
repo.base: https://gitlab.com/DPDmancul/complete-integers-agda

documentclass: book
---

# Introduction {-}

```{r, echo=F}
library(knitr)
if (knitr::is_latex_output())
  options(tinytex.engine_args = '-shell-escape')
```

\newcommand\bN{\mathbb{N}}
\newcommand\bZ{\mathbb{Z}}
\newcommand\bF{\mathbb{F}}
\newcommand\bR{\mathbb{R}}

\newcommand{\coloneqq}{\mathrel{:=}}


\newcommand\mkw[1]{\mathop{\mathrm{#1}}\nolimits}

\newcommand{\val}{\mkw{val}}
\newcommand{\Par}{\mkw{par}}


In this work we will define a superset of integers (the complete integers,
$\bZ_C$), which contains the dual of integers along parity (e.g. the odd zero, the
even one, ...). Then we will see how they form a ring and can be used to define
an TODO (parlare di x^l = |x|)


## License {-}

```{r engine="sh", echo = FALSE, results='asis'}
sed -n -e '/<!--LICENSE-->/,/<!--\/LICENSE-->/p' README.md
```

